Rhyme: A Query Language for Nested Data Structures

### 2024-12-14 paper.tex
section 4 finished

>>>>

\rhyme currently implements a C++ backend for sparse tensor algebra. As \rhyme 's type system supports multiple-width integers and floating point numbers, to maximize code reuse, we heavily utilize template in C++ to achieve polymorphism. We also utilize template meta-programming to simplify the functions used for sparse/dense tensor loading. We implement the compressed matrix and vector data structures in a C++ header. The data structure are also polymorphic and supports both the index type and value type to be template parameters.\par
We also implemented custom \emph{multi\_iterator} class used to specifically perform efficient co-iteration of multiple sparse vectors. It utilizes the N-way merge algorithm we mentioned before. Upon initialization, it takes a list of sparse vectors as arguments, and initialize the N-way merge algorithm. We overload the dereference $\ast$ operator and the increment ++ operator. So that the ++ operator will co advance the pointers in the sparse vectors until indices in all sparse vectors are the same.  The $\ast$ operator will output a pair containing the index and the list of values at this index for sparse vectors.\par
After the C++ code is generated, the host compiler like gcc or clang can be used to compile and optimize the program for execution.
\rhyme currently implements a C++ backend for sparse tensor algebra. Since \rhyme's type system supports multiple-width integers and floating-point numbers, we leverage templates in C++ to achieve polymorphism and maximize code reuse. Additionally, we utilize template metaprogramming to simplify the functions used for loading sparse and dense tensors. Compressed matrix and vector data structures are implemented in a C++ header file. These data structures are polymorphic, with both the index type and value type defined as template parameters.\par
We have also implemented a custom \emph{multi\_iterator} class specifically designed for efficient co-iteration of multiple sparse vectors. This class employs the N-way merge algorithm discussed earlier. Upon initialization, it takes a list of sparse vectors as arguments and sets up the N-way merge algorithm. The class overloads the dereference ($\ast$) operator and the increment (++) operator. The ++ operator advances the pointers in the sparse vectors until the indices in all vectors are the same, while the $\ast$ operator returns a pair consisting of the current index and a list of values at that index for the sparse vectors.\par
Once the C++ code is generated, it can be compiled and optimized for execution using host compilers such as GCC or Clang.
